Predicting sales of newly published books

### 2015-12-27 paper.tex
updating things

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm}
% FERGU: mejor tratar esto como una referencia, ya que es un texto
% Efectivamente- JJ
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are
proposed.
% no se deben usar footnotes donde debiera haber referencias. - JJ
Specifically, in order to compute the forecasting errors of the different methods, 
%FERGU: quitar este salto de linea y unirlo al párrafo de arriba.    ok
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
%*************************************** Determinar las variables a usar, según el SOM
\textbf{ TODO: add the SOM analysis }

@@

\textbf{ TODO: add the SOM analysis }
% una vez hecho, hay que hacer las ejecuciones para ese dataset.

>>>>

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations \cite{gepsoft} in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka \cite{pentaho,Witten2011} 
or R \cite{otexts,Hyndman2013}, are
proposed.
Specifically, in order to compute the forecasting errors of the different methods, 
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

%
% TODO: falta incluir aquí el análisis de los mapas SOM.
%***************************************
\textbf{ TODO: add the SOM analysis }

@@

\textbf{ TODO: add the SOM analysis }
